%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Satyendra Singh} \\ \vspace{1pt}
    \small +91 9584224133 $|$ \href{mailto:singhsatyendra885@gmail.com}{\underline{singhsatyendra885@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/satyendra}} $|$
    \href{https://github.com/...}{\underline{github.com/satyendra}}
\end{center}


%-----------Objective -----------
\section{\textbf{Professional Summary}}
Results-driven \textbf{Full Stack Developer} with 2 years of experience building web applications integrated with \textbf{IoT} and embedded systems. Expertise in developing scalable solutions using \textbf{Node.js}, \textbf{React}, and\textbf{ SQL databases}. Passionate about creating technology solutions that solve real-world problems with a focus on performance and user experience.


%-----------EXPERIENCE-----------
\section{\textbf{Professional Experience}}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{}
      {Houston System, Greater Noida, U.P.}{May 2023 - Present}
      \resumeItemListStart
        \resumeItem{\textbf{Architected} and implemented a RESTful API using Node.js and MySQL that improved learning management system data storage efficiency by 40\%.}
        \resumeItem{\textbf{Developed} a comprehensive access control system using Node.js, React, MySQL, and Docker, successfully integrating with physical hardware components including boom barriers, turnstiles, and tripods.}
        \resumeItem{\textbf{Implemented} real-time communication architecture using WebSocket, GraphQL, and Apache Kafka, reducing system latency by 60\%.}
        \resumeItem{\textbf{Engineered} hardware-software integrations using multiple protocols (TCP/IP, UDP, HTTP, WebSocket, RS-485) to create seamless connections between web applications and IoT devices.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{\textbf{Projects}}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Houston System Company Website} $|$ \emph{React.js, Tailwind CSS, TypeScript, REST API, Git}} {Jan 2025 -- Present}
            \resumeItemListStart
              \resumeItem{\textbf{Designed} and developed a responsive, SEO-optimized company website showcasing products and services.}
              \resumeItem{\textbf{Built} modular UI components using React.js and Tailwind CSS, reducing development time for new features by 35\%.}
              \resumeItem{\textbf{Implemented} WhatsApp integration for direct customer feedback, increasing customer engagement by 45\%.}
              \resumeItem{\textbf{Engineered} backend services with Node.js and Express for contact forms, product data management, and real-time customer interaction via chatbot.}
            \resumeItemListEnd

        \resumeProjectHeading
              {\textbf{Automatic Number Plate Recognition (ANPR)} $|$ \emph{RestAPI, React, GraphQL, Redux, Git}}{Sep 2024 -- Dec 2024}
              \resumeItemListStart
                \resumeItem{\textbf{Built} a role-based frontend interface using React.js, Tailwind CSS, and TypeScript with distinct admin and operator access levels.}
                \resumeItem{\textbf{Integrated} ANPR technology with parking management systems, automating vehicle logging and reducing manual entry errors by 95\%.}
                \resumeItem{\textbf{Implemented} CI/CD using TravisCI, decreasing deployment time by 70\% and eliminating deployment-related issues.}
                \resumeItem{\textbf{Developed} GraphQL and REST APIs to efficiently manage vehicle data, user roles, and system access logs.}
              \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{Mullanpur Stadium Access Control System} $|$ \emph{Node.js, MySQL, Database Indexing}}{Feb 2024 -- Aug 2024}
            \resumeItemListStart
              \resumeItem{\textbf{Designed} and deployed a multi-gate access control system serving various user categories at Mullanpur Cricket Stadium.}
              \resumeItem{\textbf{Engineered} a ticket validation system using QR and RFID scanners that processed 10,000+ tickets per event with 98\% accuracy.}
              \resumeItem{\textbf{Developed} gate-level authorization logic ensuring precise access control based on user roles and permissions.}
              \resumeItem{\textbf{Created} a centralized Flask-based backend with an optimized MySQL database for real-time validation.}
            \resumeItemListEnd
    
        \resumeProjectHeading
              {\textbf{Parking Guidace System} $|$ \emph{Node.js, React, MySQL, Docker, Git}}{June 2023 -- Jan 2024}
              \resumeItemListStart
                \resumeItem{\textbf{Developed} a full-stack application providing real-time parking availability information for multi-level parking facilities.}
                \resumeItem{\textbf{Integrated} IoT parking sensors to detect vehicle presence with 99\% accuracy and update slot occupancy in real-time.}
                \resumeItem{\textbf{Implemented} Redis for handling asynchronous tasks, reducing system load during peak usage by 50\%.}
                \resumeItem{\textbf{Created} digital signage integration showing real-time availability data on P10 LED displays.}
              \resumeItemListEnd



    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Science, in Electronics}{}
      {Lovely Professional University, Jalandhar, Punjab}{Aug. 2013 -- May 2018}
    \resumeSubheading
      {Higher Secondary Certificate}{}
      {Aadarsh Sarvodaya Higher Secondary School, Anuppur, M.P.}{Aug. 2011 -- May 2012}
    \resumeSubheading
      {Secondary School Certificate}{}
      {Aadarsh Sarvodaya High School, Anuppur, M.P.}{Aug. 2009 -- May 2010}
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:}{JavaScript (ES6+), Python, C/C++, SQL, HTML5, CSS3} \\
     \textbf{Frameworks \& Libraries:}{React.js, Node.js, Express.js, Flask, Django, Material UI, Bootstrap, Redux, Pandas, NumPy, Matplotlib} \\
     \textbf{Developer Tools:}{Git, Docker, Kubernetes, AWS Cloud Platform, CI/CD (TravisCI)} \\
     \textbf{Protocols \& APIs:}{REST, GraphQL, WebSocket, TCP/IP, UDP, HTTP, RS-485} \\
     \textbf{Other Skills:}{IoT Integration, Embedded Systems, Access Control Systems, Real-Time Data Processing} \\
     \textbf{Soft Skills:}{Problem Solving, Cross-Functional Collaboration, Technical Documentation, Project Management}
 \end{itemize}


%-------------------------------------------
\end{document}
